The Talking Heads Experiment

### 2015-04-16 chap5/chap5.tex
hyphenation, orphans, widows and some other layout updated

What cognitive architecture do agents need to engage in naming 
games? Clearly they need some sort of {\itshape associative memory} to\is{lexical memory}
store their individual lexicons.
Let us assume that agents 
can construct and recognise arbitrary consonant-vowel combinations, 
like `coba' or `wabidu', for forming words, and that they 
have a repertoire of possible meanings in the form of 
categories, for example [LEFT], [DARK], [LARGE], etc. 
The contents of the associative memory of a single agent can
be displayed in a table as follows:

\begin{table}
\begin{center}
\begin{tabular}{ l  l }
\lsptoprule
{\itshape meaning} & {\itshape form} \\ 
\midrule{}
{}[DARK] & coba \\ 
{}[LARGE] & wabidu \\ 
... & ... \\ 
\lspbottomrule
\end{tabular}
\end{center}
\caption{\label{tab:t-mem}Associative memory of a single agent.}
\end{table}
As an agent is acquiring his lexicon, there are going to 
be stages when he is not yet sure about the meaning of 
a certain form. So it must be possible for the agent
to store different 
meanings for the same form and different forms for the
same meaning. This can easily be done by extending the memory capacity
to cross-associate multiple items. Agents can then 
handle amiguity (one word can have different
meanings) and synonymy (one meaning can 
be associated with many different words).

@@

\begin{table}
\begin{center}
\begin{tabular}{c c c c  c  c  c } \lsptoprule 
& coba & zapo & bila & pama & wabidu & limiri \\ 
\midrule {}		
{}[DARK] & 0.3 & 0.2 & 0.1 & 0.8 & - & - \\ 
{}[LARGE] & - & - & - & 0.5 & 0.3 & 0.6 \\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:mem2}Example lexicon with multiple associations.}
\end{center}
\end{table}
From this table we see that the agent prefers to use the 
word `pama' for [DARK] and `limiri' for [LARGE].

@@

The operations of speaker and hearer are summarised in 
\figref{incr-decr} assuming that speaker and hearer
use both the score table above (in reality they of 
course always have different score tables). 
The speaker collects all possible
forms for a given meaning [DARK], chooses the one with the
highest score (`pama'), and transmits that form. 
The hearer collects all possible meanings for 
the transmitted form ([DARK], [LARGE]) and again chooses the one with
the highest score. If the hearer's meaning is equal to that
of the speaker's, the game succeeds. The score of 
two used associations increases and the others
decrease, implementing lateral 
inhibition. If the game fails, only the two used associations 
go down.\footnote{More or less neural realism can be introduced to 
model this associative memory. In our experiments we 
have a perfectly working memory that can store an 
association as soon as it has seen it once. This makes
theoretical investigation easier and makes it possible
to better follow the simulations and experimentations.  
An example of a neural network solution to lexical
memory is discussed in \cite{Cangelosi:1996}.}

@@

To become more familiar with the Naming Game, I will now 
go through a few examples of its application, assuming 
a group of five agents: ${\cal A}$ = $\{${\bfshape a1},{\bfshape a2},
{\bfshape a3}, {\bfshape a4}, {\bfshape a5}$\}$ and five possible shared meanings: 
\newline 
${\cal M}$ = $\{[DARK],[LARGE],[LIGHT],[SMALL],[RED]\}$. 
\newline
Here is a trace of a first game as reported by 
the commentator, when the agents do not have any lexicon at
all. 
\begin{verbatim}
Game 0 
  a5 is the speaker. a3 is the hearer. 
  a5 categorises the topic as [LIGHT]
  a5 does not have a word for [LIGHT]
\end{verbatim}
This trace lists the number of the game, the speaker, the 
hearer and the categorisation of
the topic. The speaker did not have a word and did not 
create one (because the word creation probability is 
$w_{c}=0.1$): the game has failed. In the beginning 
most games fail if the word creation rate has been set to a low rate.

In the next game shown below, the speaker is 
{\bfshape a4}, the hearer {\bfshape a5} and the topic
{}[SMALL]. Now the speaker is successful in creating a word, namely 
`di'. The hearer receives the word, does not know it,
but stores it in association with [SMALL]. The game still fails. 
\begin{verbatim}
Game 29
   a4 is the speaker. a5 is the hearer. 
   a4 categorises the topic as [SMALL]
   a4 creates a new word: di
   a5 does not know di
   a4 points to the topic
   a5 categorises the topic as [SMALL]
   a5 stores di as [SMALL]
\end{verbatim}
In game 32, something similar happens. This time {\bfshape a5} creates
a new word `pida' for [LARGE]. {\bfshape a3} does not know 
the word but stores it. 
\begin{verbatim}
Game 32
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 creates a new word: `pida'
   a5 says: pida
   a3 does not know pida
   a5 points to the topic
   a3 categorises the topic as [LARGE]
   a3 stores pida as [LARGE]
\end{verbatim}
A first success occurs in game 43, when {\bfshape a5} uses again 
`pida' for [LARGE]. {\bfshape a3} hears `pida', has associated it 
in his lexicon with [LARGE], and so the game succeeds. 
\begin{verbatim}
Game 43
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 says: pida
   a3 interprets pida as [LARGE]
   a3 points to the topic 
   a5 signals OK
\end{verbatim}
It is quite tedious to go through such games by hand. 
For large populations of agents or meanings, even the 
most diligent researcher soon loses patience. Fortunately 
it is not so difficult to implement the Naming Game model on 
a computer. This makes large-scale simulations, even with 
hundreds of agents and meanings feasable, and ensures
that they have been done correctly.
All traces and graphs of games reported in this book
have been produced by computer simulations or physical 
experiments with the Talking Heads.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l }
\lsptoprule 
{\itshape Meaning} & {\itshape Word} & {\itshape Score} \\ \midrule
{}[LARGE]& pida& 0.20\\ 
  & fobu& 0.1\\ 
{}[LIGHT]& gi& 0.0\\ 
{}[SMALL]& di & 0.10\\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem3}Associative memory of a single agent after 100 games.}
\end{center}
\end{table}
Both the words `di' and `pida' are present but with 
weak scores. There are two synonyms for 
{}[LARGE]: `pida' and `fobu', but `pida' is 
preferred. There is a word `gi' who is available 
for [LIGHT] but does not have a positive score,
because successive trials failed to yield a successful game.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l }
\lsptoprule 
{\itshape Meaning}& {\itshape Word} & {\itshape Frequency} \\ \midrule 
{}[LARGE]& pida& 0.40\\ 
{}[LIGHT]& gi & 0.60\\ 
{}[SMALL]& di & 0.40\\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem4}Population lexicon after 50 games}
\end{center}
\end{table}
This reflects a situation where 40 \%
of the agents prefers to name [LARGE] with
`pida'. 60 \% of the agents
use `gi' for [LIGHT], and 40 \% `di' for [SMALL]. 
The other meanings ([DARK] and [RED]) do not have names yet.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  c  l  l  c } \midrule 
{\itshape meaning} & {\itshape form} & {\itshape frequency} & {\itshape meaning} & {\itshape form} & {\itshape frequency}\\  
{}[DARK]& go & 1.00 & [LARGE]& pida & 1.00 \\  
{}[LIGHT]& gi & 1.00 & [SMALL]& di & 1.00 \\  
{}[RED]& ga & 1.00 & - & - & -  \\  
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem5}Consensus in group lexicon, reached after 250 games.}
\end{center}
\end{table}
Once the agents have reached this stage, the lexicon does not 
change anymore, because all agents now prefer the same word for 
each possible meaning and would never choose another one
nor encounter another one.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l  l  l  l }
\lsptoprule 
{\itshape meaning} & {\itshape form} & {\itshape frequency} & {\itshape meaning} & {\itshape form} & {\itshape frequency} \\ \midrule
{}[DARK]& dato & 1.00 & [LARGE]& biti & 0.80 \\  
{}[LIGHT]& pitu & 0.60 & [SMALL]& dopu & 1.00 \\  
{}[RED]& gabi & 1.00 & [GREEN]& gu & 0.85 \\  
{}[SQUARE]& koti & 0.50 & [RECTANGLE]& totu & 0.65 \\  
{}[LEFT]& toga & 0.90 & [BLUE]& ku & 0.80 \\  
{}[YELLOW]& gubo & 0.55 & [CHARMING]& ge & 1.00 \\  
{}[TRIANGLE]& bu & 0.85 & [SQUARE]& ba & 0.60 \\  
{}[FAST]& beke & 1.00 & [SLOW]& tu & 0.95 \\  
{}[CIRCLE]& ke & 0.75 & [RIGHT]& gaba & 0.95 \\  
{}[UP]& butu & 1.00 & [DOWN]& ki & 0.95 \\  
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem3000}Group lexicon after 3000 games.}
\end{center}
\end{table}
The lexical coherence is at this point equal to 0.835.

@@

The following vocabularies illustrate this point clearly.
The first vocabulary is taken from an agent from the
leftmost cluster in \figref{figure-agent-distribution}. 
All the words associated with a particular meaning are 
shown together with their score. 
\begin{verbatim}
{}[M0]: kube[0.88] gutida[0.00] moko[0.00]
{}[M1]: nugini[0.97] gi[0.83] majiba[0.00]
{}[M2]: go[0.98] ta[0.00]
{}[M3]: moma[0.98] ti[0.00] nudo[0.00] kene[0.00]
{}[M4]: nebu[0.98] me[0.83]
{}[M5]: tine[0.98]
\end{verbatim}
\begin{verbatim}
{}[M6]: bo[0.94] babige[0.82]
{}[M7]: mepabo[0.97] jabeto[0.71] di[0.00]
{}[M8]: kude[0.90] nado[0.00]
{}[M9]: pe[0.94] da[0.00]
{}[M10]: na[0.94] nuguge[0.90] pa[0.80] ne[0.00]
\end{verbatim}
\begin{verbatim}
{}[M11]: mu[0.98] gite[0.00] paku[0.00]
{}[M12]: gema[0.96] do[0.33] gapu[0.00]
{}[M13]: ja[0.67] jo[0.00]
{}[M14]: dodine[0.88] pibo[0.83] gije[0.00] pupeto[0.00]
{}[M15]: jiti[0.94] gato[0.64]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.98] ba[0.00]
{}[M17]: bapi[0.96] ki[0.81] damuti[1,0,0.00]
{}[M18]: kutume [0.94] bu [0.00] ni[0.00]
{}[M19]: mugu[0.95] NINU[0.50] pi[0.43] ji[0.00] tu[0.00]
\end{verbatim}
This is the vocabulary for an agent taken from the
rightmost cluster in \figref{figure-agent-distribution}:
\begin{verbatim}
{}[M0]: gutida[0.79] kube[0.00]
{}[M1]: gi[0.89] matu[0.85] pumoni[0.00]
{}[M2]: go[0.95] ta[0.20]
{}[M3]: kene[0.89] moma[0.82] nudo[0.00] koko[0.00]
{}[M4]: nebu[0.97] me[0.00] bukugo[0.00]
{}[M5]: tine[0.90]
\end{verbatim}
\begin{verbatim}
{}[M6]: babige[0.93] bo[0.00]
{}[M7]: mepabo[0.90] junipe[0.75] di[0.00]
{}[M8]: nado[0.96] kude[0.80] puto[0.00]
{}[M9]: da[0.86] nine[0.71]
{}[M10]: pa[0.87]
\end{verbatim}
\begin{verbatim}
{}[M11]: gite[0.88]
{}[M12]: gema[0.90] gapu[0.87]
{}[M13]: jo[0.96] ji[0.89] ja[0.00]
{}[M14]: dodine[0.96] pupeto[0.56] pibo[0.00] gije[0.00]
{}[M15]: jiti[0.97] gato[0.46]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.97] ba[0.83] pipebe[0.00]
{}[M17]: ki[0.97] bapi[0.00] ke[,0.00]
{}[M18]: ni[0.94] kutume[0.80] moko[0.80] mekami[0.00]
{}[M19]: ninu[0.81] mugu[0.00] pi[0.00]
\end{verbatim}
Some words (for example `tine' for [M5] or `go' for [M2]) are
shared. But generally 
there are at least two words. One word is used preferentially inside the cluster,
the other is known but preferentially used by members of another cluster. Thus
the word `mugu' for [M19] is preferred for the first object in the first
cluster and known but not preferentially used by the agent in the second cluster.
Conversely, `ninu' is preferred for the same meaning by the agent in the second
cluster, although he also knows `mugu'.
`mepabo' for [M7] belongs to the interlingua. Both agents
know and use it but they have a strong alternative `jabeto' for 
the first and `junipe' for the second agent.

>>>>

What cognitive architecture do agents need to engage in naming 
games? Clearly they need some sort of {\itshape associative memory} to\is{lexical memory}
store their individual lexicons.
Let us assume that agents 
can construct and recognise arbitrary consonant-vowel combinations, 
like `coba' or `wabidu', for forming words, and that they 
have a repertoire of possible meanings in the form of 
categories, for example [\textsc{left}], [\textsc{dark}], [\textsc{large}], etc. 
The contents of the associative memory of a single agent can
be displayed in a table as follows:

\begin{table}
\begin{center}
\begin{tabular}{ l  l }
\lsptoprule
{\itshape meaning} & {\itshape form} \\ 
\midrule{}
{}[\textsc{dark}] & coba \\ 
{}[\textsc{large}] & wabidu \\ 
... & ... \\ 
\lspbottomrule
\end{tabular}
\end{center}
\caption{\label{tab:t-mem}Associative memory of a single agent.}
\end{table}
As an agent is acquiring his lexicon, there are going to 
be stages when he is not yet sure about the meaning of 
a certain form. So it must be possible for the agent
to store different 
meanings for the same form and different forms for the
same meaning. This can easily be done by extending the memory capacity
to cross-associate multiple items. Agents can then 
handle amiguity (one word can have different
meanings) and synonymy (one meaning can 
be associated with many different words).

@@

\begin{table}
\begin{center}
\begin{tabular}{c c c c  c  c  c } \lsptoprule 
& coba & zapo & bila & pama & wabidu & limiri \\ 
\midrule {}		
{}[\textsc{dark}] & 0.3 & 0.2 & 0.1 & 0.8 & - & - \\ 
{}[\textsc{large}] & - & - & - & 0.5 & 0.3 & 0.6 \\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:mem2}Example lexicon with multiple associations.}
\end{center}
\end{table}
From this table we see that the agent prefers to use the 
word `pama' for [\textsc{dark}] and `limiri' for [\textsc{large}].

@@

The operations of speaker and hearer are summarised in 
\figref{incr-decr} assuming that speaker and hearer
use both the score table above (in reality they of 
course always have different score tables). 
The speaker collects all possible
forms for a given meaning [\textsc{dark}], chooses the one with the
highest score (`pama'), and transmits that form. 
The hearer collects all possible meanings for 
the transmitted form ([\textsc{dark}], [\textsc{large}]) and again chooses the one with
the highest score. If the hearer's meaning is equal to that
of the speaker's, the game succeeds. The score of 
two used associations increases and the others
decrease, implementing lateral 
inhibition. If the game fails, only the two used associations 
go down.\footnote{More or less neural realism can be introduced to 
model this associative memory. In our experiments we 
have a perfectly working memory that can store an 
association as soon as it has seen it once. This makes
theoretical investigation easier and makes it possible
to better follow the simulations and experimentations.  
An example of a neural network solution to lexical
memory is discussed in \cite{Cangelosi:1996}.}

@@

To become more familiar with the Naming Game, I will now 
go through a few examples of its application, assuming 
a group of five agents: ${\cal A}$ = $\{${\bfshape a1},{\bfshape a2},
{\bfshape a3}, {\bfshape a4}, {\bfshape a5}$\}$ and five possible shared meanings: 
${\cal M}$ = $\{[\textsc{dark}],[\textsc{large}],[\textsc{light}],[\textsc{small}],[\textsc{red}]\}$. 
\newline
Here is a trace of a first game as reported by 
the commentator, when the agents do not have any lexicon at
all. 
\begin{verbatim}
Game 0 
  a5 is the speaker. a3 is the hearer. 
  a5 categorises the topic as [LIGHT]
  a5 does not have a word for [LIGHT]
\end{verbatim}
This trace lists the number of the game, the speaker, the 
hearer and the categorisation of
the topic. The speaker did not have a word and did not 
create one (because the word creation probability is 
$w_{c}=0.1$): the game has failed. In the beginning 
most games fail if the word creation rate has been set to a low rate.

In the next game shown below, the speaker is 
{\bfshape a4}, the hearer {\bfshape a5} and the topic
{}[\textsc{small}]. Now the speaker is successful in creating a word, namely 
`di'. The hearer receives the word, does not know it,
but stores it in association with [\textsc{small}]. The game still fails. 
\begin{verbatim}
Game 29
   a4 is the speaker. a5 is the hearer. 
   a4 categorises the topic as [SMALL]
   a4 creates a new word: di
   a5 does not know di
   a4 points to the topic
   a5 categorises the topic as [SMALL]
   a5 stores di as [SMALL]
\end{verbatim}
In game 32, something similar happens. This time {\bfshape a5} creates
a new word `pida' for [\textsc{large}]. {\bfshape a3} does not know 
the word but stores it. 
\begin{verbatim}
Game 32
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 creates a new word: `pida'
   a5 says: pida
   a3 does not know pida
   a5 points to the topic
   a3 categorises the topic as [LARGE]
   a3 stores pida as [LARGE]
\end{verbatim}
A first success occurs in game 43, when {\bfshape a5} uses again 
`pida' for [\textsc{large}]. {\bfshape a3} hears `pida', has associated it 
in his lexicon with [\textsc{large}], and so the game succeeds. 
\begin{verbatim}
Game 43
   a5 is the speaker. a3 is the hearer. 
   a5 categorises the topic as [LARGE]
   a5 says: pida
   a3 interprets pida as [LARGE]
   a3 points to the topic 
   a5 signals OK
\end{verbatim}
It is quite tedious to go through such games by hand. 
For large populations of agents or meanings, even the 
most diligent researcher soon loses patience. Fortunately 
it is not so difficult to implement the Naming Game model on 
a computer. This makes large-scale simulations, even with 
hundreds of agents and meanings feasable, and ensures
that they have been done correctly.
All traces and graphs of games reported in this book
have been produced by computer simulations or physical 
experiments with the Talking Heads.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l }
\lsptoprule 
{\itshape Meaning} & {\itshape Word} & {\itshape Score} \\ \midrule
{}[\textsc{large}]& pida& 0.20\\ 
  & fobu& 0.1\\ 
{}[\textsc{light}]& gi& 0.0\\ 
{}[\textsc{small}]& di & 0.10\\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem3}Associative memory of a single agent after 100 games.}
\end{center}
\end{table}
Both the words `di' and `pida' are present but with 
weak scores. There are two synonyms for 
{}[\textsc{large}]: `pida' and `fobu', but `pida' is 
preferred. There is a word `gi' who is available 
for [\textsc{light}] but does not have a positive score,
because successive trials failed to yield a successful game.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l }
\lsptoprule 
{\itshape Meaning}& {\itshape Word} & {\itshape Frequency} \\ \midrule 
{}[\textsc{large}]& pida& 0.40\\ 
{}[\textsc{light}]& gi & 0.60\\ 
{}[\textsc{small}]& di & 0.40\\ 
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem4}Population lexicon after 50 games}
\end{center}
\end{table}
This reflects a situation where 40 \%
of the agents prefers to name [\textsc{large}] with
`pida'. 60 \% of the agents
use `gi' for [\textsc{light}], and 40 \% `di' for [\textsc{small}]. 
The other meanings ([\textsc{dark}] and [\textsc{red}]) do not have names yet.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  c  l  l  c } \midrule 
{\itshape meaning} & {\itshape form} & {\itshape frequency} & {\itshape meaning} & {\itshape form} & {\itshape frequency}\\  
{}[\textsc{dark}]& go & 1.00 & [\textsc{large}]& pida & 1.00 \\  
{}[\textsc{light}]& gi & 1.00 & [\textsc{small}]& di & 1.00 \\  
{}[\textsc{red}]& ga & 1.00 & - & - & -  \\  
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem5}Consensus in group lexicon, reached after 250 games.}
\end{center}
\end{table}
Once the agents have reached this stage, the lexicon does not 
change anymore, because all agents now prefer the same word for 
each possible meaning and would never choose another one
nor encounter another one.

@@

\begin{table}
\begin{center}
\begin{tabular}{l  l  l  l  l  l }
\lsptoprule 
{\itshape meaning} & {\itshape form} & {\itshape frequency} & {\itshape meaning} & {\itshape form} & {\itshape frequency} \\ \midrule
{}[\textsc{dark}]& dato & 1.00 & [\textsc{large}]& biti & 0.80 \\  
{}[\textsc{light}]& pitu & 0.60 & [\textsc{small}]& dopu & 1.00 \\  
{}[\textsc{red}]& gabi & 1.00 & [\textsc{green}]& gu & 0.85 \\  
{}[\textsc{square}]& koti & 0.50 & [\textsc{rectangle}]& totu & 0.65 \\  
{}[\textsc{left}]& toga & 0.90 & [\textsc{blue}]& ku & 0.80 \\  
{}[\textsc{yellow}]& gubo & 0.55 & [\textsc{charming}]& ge & 1.00 \\  
{}[\textsc{triangle}]& bu & 0.85 & [\textsc{square}]& ba & 0.60 \\  
{}[\textsc{fast}]& beke & 1.00 & [\textsc{slow}]& tu & 0.95 \\  
{}[\textsc{circle}]& ke & 0.75 & [\textsc{right}]& gaba & 0.95 \\  
{}[\textsc{up}]& butu & 1.00 & [\textsc{down}]& ki & 0.95 \\  
\lspbottomrule
\end{tabular}
\caption{\label{tab:t-mem3000}Group lexicon after 3000 games.}
\end{center}
\end{table}
The lexical coherence is at this point equal to 0.835.

@@

The following vocabularies illustrate this point clearly.
The first vocabulary is taken from an agent from the
leftmost cluster in \figref{figure-agent-distribution}. 
All the words associated with a particular meaning are 
shown together with their score. \todo{What do the \{ and \} mean?}
\begin{verbatim}
{}[M0]: kube[0.88] gutida[0.00] moko[0.00]
{}[M1]: nugini[0.97] gi[0.83] majiba[0.00]
{}[M2]: go[0.98] ta[0.00]
{}[M3]: moma[0.98] ti[0.00] nudo[0.00] kene[0.00]
{}[M4]: nebu[0.98] me[0.83]
{}[M5]: tine[0.98]
\end{verbatim}
\begin{verbatim}
{}[M6]: bo[0.94] babige[0.82]
{}[M7]: mepabo[0.97] jabeto[0.71] di[0.00]
{}[M8]: kude[0.90] nado[0.00]
{}[M9]: pe[0.94] da[0.00]
{}[M10]: na[0.94] nuguge[0.90] pa[0.80] ne[0.00]
\end{verbatim}
\begin{verbatim}
{}[M11]: mu[0.98] gite[0.00] paku[0.00]
{}[M12]: gema[0.96] do[0.33] gapu[0.00]
{}[M13]: ja[0.67] jo[0.00]
{}[M14]: dodine[0.88] pibo[0.83] gije[0.00] pupeto[0.00]
{}[M15]: jiti[0.94] gato[0.64]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.98] ba[0.00]
{}[M17]: bapi[0.96] ki[0.81] damuti[1,0,0.00]
{}[M18]: kutume [0.94] bu [0.00] ni[0.00]
{}[M19]: mugu[0.95] NINU[0.50] pi[0.43] ji[0.00] tu[0.00]
\end{verbatim}
This is the vocabulary for an agent taken from the
rightmost cluster in \figref{figure-agent-distribution}:
\begin{verbatim}
{}[M0]: gutida[0.79] kube[0.00]
{}[M1]: gi[0.89] matu[0.85] pumoni[0.00]
{}[M2]: go[0.95] ta[0.20]
{}[M3]: kene[0.89] moma[0.82] nudo[0.00] koko[0.00]
{}[M4]: nebu[0.97] me[0.00] bukugo[0.00]
{}[M5]: tine[0.90]
\end{verbatim}
\begin{verbatim}
{}[M6]: babige[0.93] bo[0.00]
{}[M7]: mepabo[0.90] junipe[0.75] di[0.00]
{}[M8]: nado[0.96] kude[0.80] puto[0.00]
{}[M9]: da[0.86] nine[0.71]
{}[M10]: pa[0.87]
\end{verbatim}
\begin{verbatim}
{}[M11]: gite[0.88]
{}[M12]: gema[0.90] gapu[0.87]
{}[M13]: jo[0.96] ji[0.89] ja[0.00]
{}[M14]: dodine[0.96] pupeto[0.56] pibo[0.00] gije[0.00]
{}[M15]: jiti[0.97] gato[0.46]
\end{verbatim}
\begin{verbatim}
{}[M16]: bimogu[0.97] ba[0.83] pipebe[0.00]
{}[M17]: ki[0.97] bapi[0.00] ke[,0.00]
{}[M18]: ni[0.94] kutume[0.80] moko[0.80] mekami[0.00]
{}[M19]: ninu[0.81] mugu[0.00] pi[0.00]
\end{verbatim}
Some words (for example `tine' for [M5] or `go' for [M2]) are
shared. But generally 
there are at least two words. One word is used preferentially inside the cluster,
the other is known but preferentially used by members of another cluster. Thus
the word `mugu' for [M19] is preferred for the first object in the first
cluster and known but not preferentially used by the agent in the second cluster.
Conversely, `ninu' is preferred for the same meaning by the agent in the second
cluster, although he also knows `mugu'.
`mepabo' for [M7] belongs to the interlingua. Both agents
know and use it but they have a strong alternative `jabeto' for 
the first and `junipe' for the second agent.
